Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Update Figure 3's title and adds metadata

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Question; Methodology; Data; Analysis; Manuscript;

@@

    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
    'Source Code'; 'Data File'; 'Public Repository';

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 3.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 3.eps"),
   outfile = ("../figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
```

>>>>

    node [shape = oval, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Question

    node [shape = box, style = filled, fillcolor = grey99, width = 1.2, fontname = Helvetica]
    Methodology; Data; Analysis; Manuscript;

@@

    node [shape = box, style = filled, fillcolor = grey70, width = 1.2]
    'Source Code'; 'Data File'; Metadata; 'Public Repository';

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Data->Metadata->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 3.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 3.eps"),
   outfile = ("../figures/Sparks et al Figure 3.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 3.eps")
```
